\bf Hierarchical Network Structure Promotes Dynamical Robustness

### 2015-07-22 tex/overview.tex
consistently use SCC abbreviation

\subsection{Symmetries of SCCs and their relationship to robustness}
This map $\hier$ is many-to-one and so there is a large class of
operations which leaves $\hier(G)$ invariant for a given graph $G$ \reffighiertransformations{}. These three symmetries, \reffigscc{}, represent transformations that can be performed on the interaction graph that do not change the network of SCCs to which it is associated.
For instance, we may interchange the positions of the strongly
connected components relative to each other \reffighiertransformations$a$.  Leaving the components fixed, we may move links between nodes in a component \reffighiertransformations$b$ or between components, or even add or delete links \reffighiertransformations$c$.

@@

To relate the robustness of a graph to the robustness of its SCCs, we substitute \ref{eq:singleresamplemutau} and \ref{eq:stabfactor} into \ref{eq:robustnessbygraph}, collect factors corresponding to components, decompose integrals into their respective products, collapse integrals over delta distributions, and cancel common factors between numerator and denominator.  Let $L$ denote the set of edges of $G$ that connect distinct strongly connected components.  Then, if $i \in C_\alpha$ for some SCC $C_\alpha$, we have
\begin{widetext}
\begin{equation}\label{eq:robustncessforsccs}
\begin{aligned}
\frac{\int d\mu(A) d\tau^{(1)}_i (A' \mid A) \mathcal{S}(A) \mathcal{S}(A')}
       {\int d\mu(A) \mathcal{S}(A)}
&= \frac{\begin{matrix}
  \int \prod\limits_{k \in C_\alpha} da_k\,d{a'}_k\, \rho(a_k)
    \rho_i({a'}_i) \prod\limits_{j \in C_\alpha \setminus i} \delta ({a'}_j - a_j)
    \mathcal{S}(\pi_{C_{\alpha}}(A)) \mathcal{S}(\pi_{C_{\alpha}}(A')) \times \\
 \prod\limits_{C_\beta \in \hier(G) \setminus C_\alpha} \int
   \prod\limits_{j \in C_\beta} da_k\,d{a'}_k\, \rho({a'}_j) \delta ({a'}_j - a_j)
      \mathcal{S}(\pi_{C_{\beta}}(A)) \mathcal{S}(\pi_{C_{\beta}}(A')) \times \\
 \prod\limits_{l \in L} \int da_l\,d{a'}_l\,\rho({a'}_l) \delta({a'}_l - a_l) \end{matrix}}
{\begin{matrix}\int \prod\limits_{k \in C_\alpha} da_k\,\rho(a_k) \mathcal{S}(\pi_{C_{\alpha}}(A)) \times \\
 \prod_{C_\beta \in \hier(G) \setminus C_\alpha}
   \int \prod\limits_{h \in C_\alpha} da_h,\rho(a_h) \mathcal{S}(\pi_{C_{\beta}}(A)) \times \\
 \prod\limits_{l \in L} \int da_l\,\rho(a_l) \end{matrix}} \\[1em]
&= \frac{\int \prod\limits_{k \in C_\alpha} da_k\,d{a'}_k\,\rho(a_k)
    \rho_i({a'}_i) \prod\limits_{j \in C_\alpha \setminus i} \delta ({a'}_j - a_j)
    \mathcal{S}(\pi_{C_{\alpha}}(A)) \mathcal{S}(\pi_{C_{\alpha}}(A'))}
{\int \prod\limits_{k \in C_\alpha} dk\, \rho(a_k) \mathcal{S}(\pi_{C_{\alpha}}(A))} \\
&= R(C_{\alpha}, S, \mu_\alpha, \tau^{(1)}_\alpha)
\end{aligned}
\end{equation}
\end{widetext}
where $\mu_\alpha$ and $\tau^{(1)}_\alpha$ refer to the analogues of \ref{eq:singleresamplemutau} for the subgraph $C_\alpha$ of $G$. \ref{eq:robustncessforsccs} shows that the terms in the sum over the elements of $A$, or equivalently the edges of $G$, that comprise a given SCC of $G$ reduce to the robustness of that SCC alone.  Likewise, when $i \in L$, we have
\begin{widetext}
\begin{equation}\label{eq:robustncessforsccconnect}
\begin{aligned}
\frac{\int d\mu(A) d\tau^{(1)}_i (A' \mid A) \mathcal{S}(A) \mathcal{S}(A')}
       {\int d\mu(A) \mathcal{S}(A)}
&= \frac{\begin{matrix}
  \prod\limits_{C_\alpha \in \hier(G)} \int
   \prod\limits_{j \in C_\beta} da_k\,d{a'}_k\, \rho({a'}_j) \delta ({a'}_j - a_j)
      \mathcal{S}(\pi_{C_\alpha}(A)) \mathcal{S}(\pi_{C_\alpha}(A')) \times \\
 \int da_i d{a'}_i \rho_i(a) \rho_a({a'}_i) \times
 \prod\limits_{l \in L\setminus i} \int da_l\,d{a'}_l\,\rho({a'}_l) \delta({a'}_l - a_l) \end{matrix}}
{\prod_{C_\alpha \in \hier(G)}
   \int \prod\limits_{h \in C_\alpha} da_h,\rho(a_h) \mathcal{S}(\pi_{C_\alpha}(A)) \times
 \int da_i \rho(a_i) \times
 \prod\limits_{l \in L \setminus i} \int da_l\,\rho(a_l)} \\
&= 1
\end{aligned}
\end{equation}
\end{widetext}
For each $C_{\alpha} \in \hier(G)$, there will be $d_\alpha$ values of $i$ such that $i \in C_{\alpha}$ requiring instances of \ref{eq:robustncessforsccs}; likewise, there will be $l$ values of $i$ such that $i \in L$ requiring instances of \ref{eq:robustncessforsccconnect}.  Hence, when we perform the summation over $i$ to compute the robustness of $\mathcal{F}/G$ for each $G$, we will obtain a weighted average:
\begin{equation}\label{eq:robschematic}
R = \frac{l+d_1 R_1 + d_2 R_2 + \cdots}{l+d_1 + d_2 + \cdots}.
\end{equation}
Here $R_\alpha$ is shorthand for $R(C_\alpha,S,\mu_\alpha,\tau^{(1)}_\alpha)$ and $R$ is shorthand for $R(G,S,\mu,\tau^{(1)})$.

@@

$m_0$ links between strongly connected components.  Hence, our

@@

As before, since $R(C_\alpha, S, \mu, \tau^{(m_i)}) \le 1$, we may
increase $R(G, S, \mu, \tau^{(m)})$ by increasing the maximum
possible value of $m_0$ while keeping the strongly connected
components the same.  Again, if we fix $\hier(G)$, the maximum
possible value of $m_0$ is $\sum_{(\alpha,\beta) \in \hier(G)} v_\alpha v_\beta$
whereas, if we allow it to vary, the maximum is $\frac{1}{2} ((\sum_{\alpha=1}^n
v_\alpha)^2 - \sum_{\alpha=1}^n v_\alpha^2)$, which is attained when $\hier(G_{max}) =
G_{tot}$.  Hence, we conclude that $R(G, S, \mu, \tau^{(m)}) \le
R(G_{\mathrm{max}}, S, \mu, \tau^{(m)})$.

>>>>

\subsection{Symmetries of SCCs and their relationship to robustness}
This map $\hier$ is many-to-one and so there is a large class of
operations which leaves $\hier(G)$ invariant for a given graph $G$ \reffighiertransformations{}. These three symmetries, \reffigscc{}, represent transformations that can be performed on the interaction graph that do not change the network of SCCs to which it is associated.
For instance, we may interchange the positions of the SCCs relative to each other \reffighiertransformations$a$.  Leaving the components fixed, we may move links between nodes in a component \reffighiertransformations$b$ or between components, or even add or delete links \reffighiertransformations$c$.

@@

To relate the robustness of a graph to the robustness of its SCCs, we substitute \ref{eq:singleresamplemutau} and \ref{eq:stabfactor} into \ref{eq:robustnessbygraph}, collect factors corresponding to components, decompose integrals into their respective products, collapse integrals over delta distributions, and cancel common factors between numerator and denominator.  Let $L$ denote the set of edges of $G$ that connect distinct SCCs.  Then, if $i \in C_\alpha$ for some SCC $C_\alpha$, we have
\begin{widetext}
\begin{equation}\label{eq:robustncessforsccs}
\begin{aligned}
\frac{\int d\mu(A) d\tau^{(1)}_i (A' \mid A) \mathcal{S}(A) \mathcal{S}(A')}
       {\int d\mu(A) \mathcal{S}(A)}
&= \frac{\begin{matrix}
  \int \prod\limits_{k \in C_\alpha} da_k\,d{a'}_k\, \rho(a_k)
    \rho_i({a'}_i) \prod\limits_{j \in C_\alpha \setminus i} \delta ({a'}_j - a_j)
    \mathcal{S}(\pi_{C_{\alpha}}(A)) \mathcal{S}(\pi_{C_{\alpha}}(A')) \times \\
 \prod\limits_{C_\beta \in \hier(G) \setminus C_\alpha} \int
   \prod\limits_{j \in C_\beta} da_k\,d{a'}_k\, \rho({a'}_j) \delta ({a'}_j - a_j)
      \mathcal{S}(\pi_{C_{\beta}}(A)) \mathcal{S}(\pi_{C_{\beta}}(A')) \times \\
 \prod\limits_{l \in L} \int da_l\,d{a'}_l\,\rho({a'}_l) \delta({a'}_l - a_l) \end{matrix}}
{\begin{matrix}\int \prod\limits_{k \in C_\alpha} da_k\,\rho(a_k) \mathcal{S}(\pi_{C_{\alpha}}(A)) \times \\
 \prod_{C_\beta \in \hier(G) \setminus C_\alpha}
   \int \prod\limits_{h \in C_\alpha} da_h,\rho(a_h) \mathcal{S}(\pi_{C_{\beta}}(A)) \times \\
 \prod\limits_{l \in L} \int da_l\,\rho(a_l) \end{matrix}} \\[1em]
&= \frac{\int \prod\limits_{k \in C_\alpha} da_k\,d{a'}_k\,\rho(a_k)
    \rho_i({a'}_i) \prod\limits_{j \in C_\alpha \setminus i} \delta ({a'}_j - a_j)
    \mathcal{S}(\pi_{C_{\alpha}}(A)) \mathcal{S}(\pi_{C_{\alpha}}(A'))}
{\int \prod\limits_{k \in C_\alpha} dk\, \rho(a_k) \mathcal{S}(\pi_{C_{\alpha}}(A))} \\
&= R(C_{\alpha}, S, \mu_\alpha, \tau^{(1)}_\alpha)
\end{aligned}
\end{equation}
\end{widetext}
where $\mu_\alpha$ and $\tau^{(1)}_\alpha$ refer to the analogues of \ref{eq:singleresamplemutau} for the subgraph $C_\alpha$ of $G$. \ref{eq:robustncessforsccs} shows that the terms in the sum over the elements of $A$, or equivalently the edges of $G$, that comprise a given SCC of $G$ reduce to the robustness of that SCC alone.  Likewise, when $i \in L$, we have
\begin{widetext}
\begin{equation}\label{eq:robustncessforsccconnect}
\begin{aligned}
\frac{\int d\mu(A) d\tau^{(1)}_i (A' \mid A) \mathcal{S}(A) \mathcal{S}(A')}
       {\int d\mu(A) \mathcal{S}(A)}
&= \frac{\begin{matrix}
  \prod\limits_{C_\alpha \in \hier(G)} \int
   \prod\limits_{j \in C_\beta} da_k\,d{a'}_k\, \rho({a'}_j) \delta ({a'}_j - a_j)
      \mathcal{S}(\pi_{C_\alpha}(A)) \mathcal{S}(\pi_{C_\alpha}(A')) \times \\
 \int da_i d{a'}_i \rho_i(a) \rho_a({a'}_i) \times
 \prod\limits_{l \in L\setminus i} \int da_l\,d{a'}_l\,\rho({a'}_l) \delta({a'}_l - a_l) \end{matrix}}
{\prod_{C_\alpha \in \hier(G)}
   \int \prod\limits_{h \in C_\alpha} da_h,\rho(a_h) \mathcal{S}(\pi_{C_\alpha}(A)) \times
 \int da_i \rho(a_i) \times
 \prod\limits_{l \in L \setminus i} \int da_l\,\rho(a_l)} \\
&= 1
\end{aligned}
\end{equation}
\end{widetext}
For each $C_{\alpha} \in \hier(G)$, there will be $d_\alpha$ values of $i$ such that $i \in C_{\alpha}$ requiring instances of \ref{eq:robustncessforsccs}; likewise, there will be $l$ values of $i$ such that $i \in L$ requiring instances of \ref{eq:robustncessforsccconnect}.  Hence, when we perform the summation over $i$ to compute the robustness of $\mathcal{F}/G$ for each $G$, we will obtain a weighted average:
\begin{equation}\label{eq:robschematic}
R = \frac{l+d_1 R_1 + d_2 R_2 + \cdots}{l+d_1 + d_2 + \cdots}.
\end{equation}
Here $R_\alpha$ is shorthand for $R(C_\alpha,S,\mu_\alpha,\tau^{(1)}_\alpha)$ and $R$ is shorthand for $R(G,S,\mu,\tau^{(1)})$.

@@

$m_0$ links between SCCs.  Hence, our

@@

As before, since $R(C_\alpha, S, \mu, \tau^{(m_i)}) \le 1$, we may
increase $R(G, S, \mu, \tau^{(m)})$ by increasing the maximum
possible value of $m_0$ while keeping the SCCs the same.  Again, if we fix $\hier(G)$, the maximum
possible value of $m_0$ is $\sum_{(\alpha,\beta) \in \hier(G)} v_\alpha v_\beta$
whereas, if we allow it to vary, the maximum is $\frac{1}{2} ((\sum_{\alpha=1}^n
v_\alpha)^2 - \sum_{\alpha=1}^n v_\alpha^2)$, which is attained when $\hier(G_{max}) =
G_{tot}$.  Hence, we conclude that $R(G, S, \mu, \tau^{(m)}) \le
R(G_{\mathrm{max}}, S, \mu, \tau^{(m)})$.
